---
title: "Plots"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(p8105.datasets)
library(plotly)
data(rest_inspec)
rest_inspec
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A: Distribution of restaurant scores by borough

```{r}
plot1 = rest_inspec %>%
  drop_na(score) %>%
  filter(boro %in% c("BRONX", "BROOKLYN", "MANHATTAN", "QUEENS", "STATEN ISLAND"),
         score != "-1",
         score != "-2") %>%
  plot_ly(
    y = ~score,
    color = ~boro,
    type = "box"
  )

plot1
```

Column {data-width=350}

Here, we are looking at the distribution of scores, stratified by borough. We see that each borough has about the same median score (14-16), which gives the median restaurant grade of B. This shows that there is not a dramatic difference in the distribution of scores by neighborhood. 

-----------------------------------------------------------------------

### Chart B: Numbers of Critical/Not Critical flags stratified by my 5 favorite types of food

```{r}
distribution = rest_inspec %>%
  select(boro, cuisine_description, critical_flag) %>%
  filter(cuisine_description %in% c("Pizza", "Seafood", "Italian", "Chinese", "American"),
         critical_flag %in% c("Critical", "Not Critical")) %>%
  group_by(critical_flag) %>%
  count(cuisine_description) %>%
  group_by(cuisine_description) %>%
  rename(Number = n,
         Cuisine_Description = cuisine_description) %>%
  plot_ly(
    x = ~Cuisine_Description,
    y = ~Number,
    color = ~critical_flag,
    type = "bar")
distribution
```

This bar graph looks at my 5 favorite types of food; American, Chinese, Italian, Pizza, and Seafood. This graph shows the numbers of critical and not critical flags on each type of food. To obtain this graph, I excluded critical flag values of "Not Applicable" in order to clearly see the difference in numbers of critical and not critical citations.  

### Chart C: Distribution of scores across all boroughs

```{r}
critical = rest_inspec %>%
  filter(score != "-1",
         score != "-2") %>%
  plot_ly(
    x = ~score,
    type = "histogram")
critical
```
This histogram is pretty basic; we are looking at the distribution of scores across all boroughs. The score with the highest number of observations is 12, with 39,368 individual observations. This would give those restaurants a grade of A. The lowest score was 0, which would also yield a grade of A. The highest score was 151, which would give a score of F. 

